Contextual Identity: A Framework for Usable Privacy

### 2012-10-12 paper.tex
Updated Definitions section

\section{Definitions}
Let
\begin{itemize}
\item $R$ be a set of actors and their relationships to the user
\item $T$ be a set of tasks and their side-effects when performed in service of
$R$
\item $P$ an impression that actors in $R$ have of the user when performing tasks in $T$
\end{itemize}
Let a \textbf{contextual identity} $I$ be a loose coupling of $(R, T, P)$.
A user may have multiple of these. These identities change over time, as users
form and dissolve relationships, and focus on different sets of tasks. The
desirable outcome is that the user can accomplish tasks in $T$ while being able
to predict $R$ and $P$.
%predict rather than "control" is deliberate, since a user can't realistically
%expect to engage in behavior that violates social norms and give whatever
%impression they want

This definition focusses on relationships because most privacy concerns stem
from causing problems with people the users knows~\cite{wang}. This definition
focusses on tasks because users are task-oriented, and it is easy to map user
actions (page navigation, sending email, posting, filling forms) to tasks.
(include?) The definitions of $R$ and $P$ are deliberately underspecified, as
this is work in progress.

>>>>

\section{Definitions}

\begin{definition}
  Given:
  \begin{itemize}
    \item $R$, a set of actors and their relationships to the user
    \item $T$, a set of tasks and their side-effects
    \item $p$, an identity projected by a user or perceived by actors in $R$
  \end{itemize}
\medskip

  We define a Contextual Identity $I = \{R,T,p\}$, where a user is performing tasks $T$ in view of or interaction with actors in $R$, while representing himself as identity $p$.
\end{definition}

A user may have multiple contextual identites $I$. These identities change over
time, as users form and dissolve relationships, and focus on different sets of
tasks. The user's goal is that the user can accomplish tasks in $T$, interact
with those in $R$ and claim to be $p$  while being able to predict and assert
control over as much of $I$ as possible.

Our definition focuses on relationships because most privacy concerns stem
from causing an unexpected exchange of data with people the users
knows~\cite{wang}. Tasks are key because users are task-oriented, and it is
easy to map user actions (page navigation, sending email, posting, filling
forms) to tasks.  The definition of $R$ is deliberately underspecified, as this
is work in progress.

\begin{definition}
  A Contextual Identity Violation occurs when a user's contextual identity parameters $R,T,P$ are controlled by others.  When a user's tasks are shared with the wrong set $R$, the wrong projected identifier $p$ is employed, or a user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a violation of the integrity of Contextual Identity occurs.
\end{definition}

Using these definitions, we characterize different types of violation by what part of the contextual identity the user cannot control, and then show how control can be reasserted by a user who employs various mitigation tools.
